Evolution of the AGN UV luminosity function

### 2017-09-13 Paper/paper.tex
Update text

%% \section{Introduction}

%% Possible outline of paper:

%% \begin{enumerate}
%% \item Introduction 
%% \item Data set
%% \item QLF 
%%   \begin{enumerate}
%%   \item at specific redshifts 
%%   \item global model 
%%   \end{enumerate}
%% \item Contribution to reionizatin 
%% \item Conclusion 
%% \end{enumerate}

%% \noindent Optional possibilities:

%% \begin{enumerate}
%% \item Bolometric LF
%% \item PLE, PDE, etc?
%% \item Quantitative model fit test 
%% \item BH growth 
%% \item Comparison with galaxies 
%% \end{enumerate}

@@

\begin{table*}
  % In published version of this table, we could remove file names and add data homogenisation in Notes.
  % Add z ~ 7 qso when you add it to analysis
  % See data.tex for a version of this table that includes file names
  \caption{Quasar data sets}
  \label{tab:samples}
  \begin{tabular}{crcllrSl}
    \hline
    & ID & $z$ & Survey & Reference & Number & {Area} & Notes \\
    & & & & & of quasars & {(deg$^2$)} & \\
    \hline
    1. & 13 & 0.1--2.2 & SDSS DR7 & \citet{2006AJ....131.2766R} & 48664 & 6248.0 & \\
    2. & 15 & 0.4--2.6 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 3663 & 64.2 & \\
    3. & 15  & 0.4--2.6 & --- NGP & \citet{2009MNRAS.392...19C} & 8153 & 127.7 & \\
    4. &  1 & 2.2--3.5 & BOSS DR9 & \citet{2013ApJ...773...14R} & 23301 & 2236.0 & \\
    5. & 13 & 3.7--4.7 & SDSS DR7 & \citet{2006AJ....131.2766R} & 1785 & 6248.0 & Restricted to $z<4.7$ \\
    6. & 17 & 4.7--5.4 & SDSS+WISE & \citet{2016ApJ...829...33Y} & 99 & 14555.0 & Overlaps with 8 for $M_{1450}<-26.73$ \\
    7. &  8 & 4.7--5.1 & SDSS DR7 & \citet{2013ApJ...768..105M} & 148 & 6248.0 & \\
    8. &  8 & 4.7--5.1 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 52 & 235.0 & \\
    9. &  8 & 5.1--5.5 & --- DR7 Extended & \citet{2013ApJ...768..105M} & 28 & 6248.0 & \\
    10. & 8 & 5.1--5.4 & ---  Stripe 82 Extended & \citet{2013ApJ...768..105M} & 10 & 235.0 & \\
    11. & 6 & 3.7--4.8 & NDWFS & \citet{2011ApJ...728L..26G} & 12 & 1.71 & \\
    12. & 6 & 3.8--5.1 & DLS & \citet{2011ApJ...728L..26G} & 12 & 2.05 & \\
    13. & 7 & 4.1--6.3 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 & Rescaled selection probabilities \\
    14. & 18 & 5.8--6.4 & --- Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 & \\
    15. & 18 & 5.9--6.1 & --- Overlap & \citet{2016ApJ...833..222J} & 10 & 4223.0 & \\
    16. & 18 & 5.7--6.1 & --- Stripe 82 & \citet{2016ApJ...833..222J} & 13 & 277.0 & \\
    17. & 10 & 6.0 & CFHQS Deep & \citet{2010AJ....139..906W} & 1 & 4.47 & \\
    18. & 10 & 5.9--6.4 & --- Very Wide & \citet{2010AJ....139..906W} & 16 & 494.0 & \\
    19. & 11 & 6.0--6.2 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 & \\
  \end{tabular}
\end{table*}

@@

In a magnitude bin $[M_\mathrm{min}, M_\mathrm{max})$, and redshift
  bin $[z_\mathrm{min}, z_\mathrm{max})$, we define the luminosity
    function as \citep{2000MNRAS.311..433P}
  \begin{equation}
    \phi \equiv \frac{N}{V_\mathrm{bin}},
  \end{equation}
  where $N$ is the number of quasars with magnitude
  $M_\mathrm{min}\leq M<M_\mathrm{max}$ and redshift
  $z_\mathrm{min}\leq z<z_\mathrm{max}$, and
  \begin{equation}
    V_\mathrm{bin} = \int_{M_\mathrm{min}}^{M_\mathrm{max}}dM\int_{z_\mathrm{min}}^{z_\mathrm{max}}dz\, f(M, z)\,\frac{dV}{dz},
    \label{eqn:vi}
  \end{equation}
  is the effective volume of the bin.  Here $f(M,z)$ is the quasar
  selection probability, which includes incompleteness.  Inclusion of
  the selection probability in Equation~(\ref{eqn:vi}) accounts for
  what have been referred to as ``incomplete bins'' in the literature.
  The comoving volume element $dV/dz$ is given by
  \begin{equation}
    \frac{dV}{dz}=\frac{dV}{dz\,d\Omega}\cdot A\cdot\frac{4\pi}{41253},
  \end{equation}
  where $A$ is the survey area in deg$^2$, and \citep{1999astro.ph..5116H}
  \begin{equation}
    \frac{dV}{dz\,d\Omega}=\frac{c}{H_0}\frac{d_L(z)^2}{(1+z)^2\sqrt{\Omega_m(1+z)^3+\Omega_\Lambda}},
    \label{eqn:dvdzdo}
  \end{equation}
  denotes the comoving volume element per unit solid angle.  The
  luminosity distance $d_L$ is given by
  \begin{equation}
    d_L(z)=(1+z)\frac{c}{H_0}\int_0^z\frac{dz}{\sqrt{\Omega_m(1+z)^3+\Omega_\Lambda}}.
    \label{eqn:dl}
  \end{equation}
  Equations~(\ref{eqn:dvdzdo}) and (\ref{eqn:dl}) assume a flat
  Universe ($\Omega_k=0$).  The luminosity function $\phi$ has units
  of $\mathrm{cMpc}^{-3}\mathrm{mag}^{-1}$.  We evaluate the double
  integral in Equation~(\ref{eqn:vi}) by the Euler method, i.e., by
  simply summing over the ``tiles'' of the selection function map.  We
  do not interpolate between the redshift and luminosity values of
  neighbouring tiles.  This may result in $V_i=0$ for some quasars, in
  which case we remove them from our analysis.  Figure~\ref{fig:boss}
  shows the luminosity function derived in this way for the BOSS DR9
  colour-selected sample of 23,301 quasars, in comparison with the
  published luminosity function of \citet{2013ApJ...773...14R}.
  Figure~\ref{fig:sdss} shows the luminosity function of a sample of
  15,179 quasars from the SDSS DR3 in comparison with the published
  luminosity function of \citet{2006AJ....131.2766R}.

  % Describe how we derive error bars.

  \section{Fitting procedure}

  We model the quasar luminosity function as a double power law given
  by \citep{1988MNRAS.235..935B, 1995ApJ...438..623P, 2000MNRAS.317.1014B}
  \begin{equation}
    \phi(M) = \frac{\phi_*}{10^{0.4(\alpha+1)(M-M_*)}+10^{0.4(\beta+1)(M-M_*)}},
\label{eqn:dpl}
\end{equation}
where all magnitudes are absolute magnitudes at rest-frame 1450~{\AA}.  
The luminosity function $\phi$ gives the comoving number density of
quasars per unit magnitude.  It usually has units of
mag$^{-1}$cMpc$^{-3}$.  Equation~(\ref{eqn:dpl}) has four free
parameters: the amplitude $\phi_*$, the ``break'' $M_*$, the faint-end
slope $\beta$, and the bright-end slope $\alpha$.  The likelihood
function can be written as \citep{2001AJ....121...54F}
\begin{equation}
  \mathcal{L}=\prod_{i,j}\frac{e^{-\mu_{ij}}\mu_{ij}^{n_{ij}}}{n_{ij}!},
  \label{eqn:lhood}
\end{equation}
where $n_{ij}$ is the number of quasars observed in the $(M_i, z_j)$
bin, and
\begin{equation}
  \mu_{ij}= \int_{M_i}^{M_{i+1}}dM\int_{z_i}^{z_{i+1}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz},
\end{equation}
is the average number of quasars expected in the $(M_i, z_j)$ bin
given the luminosity function $\phi(M,z)$.  To obtain the maximum
likelihood solution for the luminosity functin parameters, we minimise
the function
\begin{equation}
  S = -2\ln\mathcal{L}.
\end{equation}
In the limit of infinitesimal bins, $n_{ij}=0$ or $1$, in which case
Equation~(\ref{eqn:lhood}) can be simplified and we can write \citep{1983ApJ...269...35M}
\begin{multline}
  S = -2\sum_{i=1}^N\ln\phi(M_i, z_i)\\+2\int_{M_\mathrm{min}}^{M_\mathrm{max}}dM\int_{z_\mathrm{min}}^{z_\mathrm{max}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz},
\end{multline}
where $N$ is the total number of quasars in the sample and the
integral in the second term on the right hand side is now on the full
range of $M$ and $z$.

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{boss.pdf}
  \end{center}
  \caption{Comparison of LF derived by our method with the published
    LF of \citet{2013ApJ...773...14R} for the BOSS DR9 color-selected
    sample. There are 23,301 quasars in this sample ($2.2<z<3.5$).  Of
    these, 231 quasars have $V_i=0$ and are dropped from the
    analysis.}
  \label{fig:boss}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{sdss.pdf}
  \end{center}
  \caption{Comparison with the published LF of
    \citet{2006AJ....131.2766R} for SDSS DR3.  There are 15,343
    quasars in this sample, of which 155 quasars have $z<0.3$ and 9
    quasars have $z>5$.  Of the remaining 15179 quasars with
    $0.3<z<5$, 60 quasars have $V_i=0$ and are dropped from the
    analysis.  As a result, the green points above contain 15,119
    quasars.  The red circles contain 14,953 quasars.}
  \label{fig:sdss}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.6\textwidth,keepaspectratio]{mcgreer.pdf}
  \end{center}
  \caption{Comparison with the published LF of
    \citet{2013ApJ...768..105M} for $4.7\leq z<5.1$.  There are 148
    quasars in their DR7 sample and 52 quasars in the Stripe 82
    sample. Of these 1 quasar from the Stripe 82 sample has $V_i=0$.
    The published samples of \citet{2013ApJ...768..105M} have 146 and
    51 quasars.}
  \label{fig:mcgreer}
\end{figure*}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth]{glikman3.pdf}
  \end{center}
  \caption{Attempts at reproducing Glikman's published LF.  Panels (a)
    and (b) use her volume calculations.  Panels (c)--(e) use our
    volume calculations.  Various corrections incorporated by Gabor
    are in panels (c)--(e).  Red open circles in all panels are
    Glikman's published values; I cannot reproduce them in any of the
    panels.  All luminosity function in this version of the draft use
    Gabor's October data from panel (d).}
  \label{fig:glikman}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth]{giallongo2.pdf}
  \end{center}
  \caption{Giallongo's LF when selection function is taken to be
    $\phi_\mathrm{corr}/\phi$ from their paper.  This plots shows that
    additional correction is required, which has been incorporated in
    our LFs.}
  \label{fig:giallongo}
\end{figure*}

@@

>>>>

%% * Possible outline of paper:
%% 
%% Introduction 
%% Data
%% Method
%%   Individual fits
%%   Global fits
%% Contribution to reionizatin 
%% Conclusions
%% 
%% * Optional possibilities:
%%
%% Bolometric LF
%% Public code description 
%% More global models: PLE, PDE, Trenti, White-Conroy
%% Goodness of fit 
%% BH growth 
%% Comparison with galaxy LF
%% Comparison with previous work

@@

\begin{table*}
  % In published version of this table, we could remove file names and add data homogenisation in Notes.
  % Add z ~ 7 qso when you add it to analysis
  % See data.tex for a version of this table that includes file names
  \caption{Quasar data sets}
  \label{tab:samples}
  \begin{tabular}{crcllrSl}
    \hline
    & ID & $z$ & Survey & Reference & Number & {Area} & Notes \\
    & & & & & of quasars & {(deg$^2$)} & \\
    \hline
    1. & 13 & 0.1--2.2 & SDSS DR7 & \citet{2006AJ....131.2766R} & 48664 & 6248.0 & \\
    2. & 15 & 0.4--2.6 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 3663 & 64.2 & \\
    3. & 15  & 0.4--2.6 & --- NGP & \citet{2009MNRAS.392...19C} & 8153 & 127.7 & \\
    4. &  1 & 2.2--3.5 & BOSS DR9 & \citet{2013ApJ...773...14R} & 23301 & 2236.0 & \\
    5. & 13 & 3.7--4.7 & SDSS DR7 & \citet{2006AJ....131.2766R} & 1785 & 6248.0 & Restricted to $z<4.7$ \\
    6. & 17 & 4.7--5.4 & SDSS+WISE & \citet{2016ApJ...829...33Y} & 99 & 14555.0 & Overlaps with 8 for $M_{1450}<-26.73$ \\
    7. &  8 & 4.7--5.1 & SDSS DR7 & \citet{2013ApJ...768..105M} & 148 & 6248.0 & \\
    8. &  8 & 4.7--5.1 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 52 & 235.0 & \\
    9. &  8 & 5.1--5.5 & --- DR7 Extended & \citet{2013ApJ...768..105M} & 28 & 6248.0 & \\
    10. & 8 & 5.1--5.4 & ---  Stripe 82 Extended & \citet{2013ApJ...768..105M} & 10 & 235.0 & \\
    11. & 6 & 3.7--4.8 & NDWFS & \citet{2011ApJ...728L..26G} & 12 & 1.71 & \\
    12. & 6 & 3.8--5.1 & DLS & \citet{2011ApJ...728L..26G} & 12 & 2.05 & \\
    13. & 7 & 4.1--6.3 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 & Rescaled selection probabilities \\
    14. & 18 & 5.8--6.4 & --- Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 & \\
    15. & 18 & 5.9--6.1 & --- Overlap & \citet{2016ApJ...833..222J} & 10 & 4223.0 & \\
    16. & 18 & 5.7--6.1 & --- Stripe 82 & \citet{2016ApJ...833..222J} & 13 & 277.0 & \\
    17. & 10 & 6.0 & CFHQS Deep & \citet{2010AJ....139..906W} & 1 & 4.47 & \\
    18. & 10 & 5.9--6.4 & --- Very Wide & \citet{2010AJ....139..906W} & 16 & 494.0 & \\
    19. & 11 & 6.0--6.2 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 & \\
    20. & 19 & 6.5--7.4 & UKIDSS & \citet{2011Natur.474..616M} & 1 & 3370.0 & \\
    21. & 19 & 6.5--7.4 & UKIDSS & \citet{2007MNRAS.376L..76V} & 1 & 3370.0 & \\
  \end{tabular}
\end{table*}

@@

Given quasar luminosities and estimates for survey completeness, we
begin our analysis by first deriving luminosity functions binned both
in redshift and magnitude.  In this discussion all magnitudes are
absolute magnitudes at rest-frame 1450~{\AA}.

% Put that sentence about magnitudes in the introduction.

\subsection{Binned luminosity function estimates}

In a magnitude bin $[M_\mathrm{min}, M_\mathrm{max})$, and redshift
  bin $[z_\mathrm{min}, z_\mathrm{max})$, we define the luminosity
    function as \citep{2000MNRAS.311..433P}
  \begin{equation}
    \phi \equiv \frac{N}{V_\mathrm{bin}},
  \end{equation}
  where $N$ is the number of quasars with magnitude
  $M_\mathrm{min}\leq M<M_\mathrm{max}$ and redshift
  $z_\mathrm{min}\leq z<z_\mathrm{max}$, and
  \begin{equation}
    V_\mathrm{bin} = \int_{M_\mathrm{min}}^{M_\mathrm{max}}dM\int_{z_\mathrm{min}}^{z_\mathrm{max}}dz\, f(M, z)\,\frac{dV}{dz},
    \label{eqn:vi}
  \end{equation}
  is the effective volume of the bin.  Here $f(M,z)$ is the quasar
  selection probability, which includes incompleteness.  Inclusion of
  the selection probability in Equation~(\ref{eqn:vi}) accounts for
  what are sometimes called ``incomplete bins''
  \citep{2006AJ....131.2766R}.  The comoving volume element $dV/dz$ is
  given by
  \begin{equation}
    \frac{dV}{dz}=\frac{dV}{dz\,d\Omega}\cdot A\cdot\frac{4\pi}{41253},
  \end{equation}
  where $A$ is the survey area in deg$^2$, and 
  \begin{equation}
    \frac{dV}{dz\,d\Omega}=\frac{c}{H_0}\frac{d_L(z)^2}{(1+z)^2\sqrt{\Omega_m(1+z)^3+\Omega_\Lambda}},
    \label{eqn:dvdzdo}
  \end{equation}
  denotes the comoving volume element per unit solid angle
  \citep{1999astro.ph..5116H}.  The luminosity distance $d_L$ is given
  by
  \begin{equation}
    d_L(z)=(1+z)\frac{c}{H_0}\int_0^z\frac{dz}{\sqrt{\Omega_m(1+z)^3+\Omega_\Lambda}}.
    \label{eqn:dl}
  \end{equation}
  Equations~(\ref{eqn:dvdzdo}) and (\ref{eqn:dl}) assume a flat
  Universe ($\Omega_k=0$).  The luminosity function $\phi$ has units
  of $\mathrm{cMpc}^{-3}\mathrm{mag}^{-1}$.  We evaluate the double
  integral in Equation~(\ref{eqn:vi}) by the Euler method, i.e., by
  simply summing over the ``tiles'' of the selection function map,
  without interpolating between the redshift and luminosity values of
  neighbouring tiles.  This may result in $V_i=0$ for some quasars, in
  which case we remove them from our analysis.

  In each bin, we estimate the uncertainty in the luminosity function
  by assuming Poisson statistics \citep{1986ApJ...303..336G}.  The
  resultant binned luminosity function estimates are shown by the
  points in Figures \ref{fig:mosaic} and \ref{fig:mosaic2}.  These
  agree quite well with the published luminosity functions by these
  surveys.

  % Do we want to give the details of how good/bad this agreement
  % actually is?

  %% Figure~\ref{fig:boss}
  %% shows the luminosity function derived in this way for the BOSS DR9
  %% colour-selected sample of 23,301 quasars, in comparison with the
  %% published luminosity function of \citet{2013ApJ...773...14R}.
  %% Figure~\ref{fig:sdss} shows the luminosity function of a sample of
  %% 15,179 quasars from the SDSS DR3 in comparison with the published
  %% luminosity function of \citet{2006AJ....131.2766R}.

\subsection{Luminosity function estimates in redshift bins}

As our next step, we stop binning the quasars in luminosity, and only
bin them in redshifts.  In each redshift bin, we model the quasar
luminosity function as a double power law given by
\citep{1988MNRAS.235..935B, 1995ApJ...438..623P, 2000MNRAS.317.1014B}
\begin{equation}
  \phi(M) =
  \frac{\phi_*}{10^{0.4(\alpha+1)(M-M_*)}+10^{0.4(\beta+1)(M-M_*)}}.
  \label{eqn:dpl}
\end{equation}
Equation~(\ref{eqn:dpl}) has four free parameters: the amplitude
$\phi_*$, the ``break'' $M_*$, the faint-end slope $\beta$, and the
bright-end slope $\alpha$.  We obtain posterior probability
distributions for these parameters using MCMC \citep[e.g.,][]{jaynes}.
The joint posterior probability distribution of the model parameters
is then written as
\begin{multline}
  p(\phi_*, M_*, \alpha, \beta | \{M_i, z_i\}) \propto \\ p(\phi_*, M_*, \alpha, \beta)p(\{M_i, z_i\} | \phi_*, M_*, \alpha, \beta),
\end{multline}
where the constant of proportionality is independent of the luminosity
function parameters, and $\{M_i, z_i\}$ denotes the complete quasar
data.  We use a uniform prior distribution $p(\phi_*, M_*, \alpha,
\beta)$ and assume that the likelihood
\begin{equation}
  \mathcal{L}\equiv p(\{M_i, z_i\} | \phi_*, M_*, \alpha, \beta)
\end{equation}
is given by $\phi(M)$ with suitable normalisation.  That is the
negative logarithm of the likelihood $S\equiv -2\ln\mathcal{L}$ can be
written as
\begin{multline}
  S = -2\sum_{i=1}^N\ln\phi(M_i, z_i)\\+2\int_{M_\mathrm{min}}^{M_\mathrm{max}}dM\int_{z_\mathrm{min}}^{z_\mathrm{max}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz}.
  \label{eqn:S}
\end{multline}
where $N$ is the total number of quasars in the sample and the
integral in the second term on the right hand side is on the 
surveyed range of $M$ and $z$.

Another way of understanding the above likelihood is as limit of the
Poisson likelihood in luminosity and redshift bins
\citep{1983ApJ...269...35M, 2001AJ....121...54F}.  We can write the
probability of observing $n_{ij}$ quasars in the $(M_i, z_j)$ bin as
the Poisson distribution
\begin{equation}
  \mathcal{L}=\prod_{i,j}\frac{e^{-\mu_{ij}}\mu_{ij}^{n_{ij}}}{n_{ij}!},
  \label{eqn:lhood}
\end{equation}
where 
\begin{equation}
  \mu_{ij}= \int_{M_i}^{M_{i+1}}dM\int_{z_j}^{z_{j+1}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz},
\end{equation}
is the average number of quasars expected in the $(M_i, z_j)$ bin
given the luminosity function $\phi(M,z)$.  In the limit of
infinitesimal bins, $n_{ij}=0$ or $1$, in which case
Equation~(\ref{eqn:lhood}) can be simplified and we can get
Equation~(\ref{eqn:S}).

Our estimates for the luminosity function in several redshift bins are
shown in Figures \ref{fig:mosaic} and \ref{fig:mosaic2}.  The median
of the posterior is shown as the best fit model.  Yellow curves show a
random draw from the posterior.

\subsection{Luminosity function estimate without binning}

Finally, we obtain estimates of the luminosity function.

@@

%% \begin{figure*}
%%   \begin{center}
%%     \includegraphics[width=\textwidth,keepaspectratio]{boss.pdf}
%%   \end{center}
%%   \caption{Comparison of LF derived by our method with the published
%%     LF of \citet{2013ApJ...773...14R} for the BOSS DR9 color-selected
%%     sample. There are 23,301 quasars in this sample ($2.2<z<3.5$).  Of
%%     these, 231 quasars have $V_i=0$ and are dropped from the
%%     analysis.}
%%   \label{fig:boss}
%% \end{figure*}

%% \begin{figure*}
%%   \begin{center}
%%     \includegraphics[width=\textwidth,keepaspectratio]{sdss.pdf}
%%   \end{center}
%%   \caption{Comparison with the published LF of
%%     \citet{2006AJ....131.2766R} for SDSS DR3.  There are 15,343
%%     quasars in this sample, of which 155 quasars have $z<0.3$ and 9
%%     quasars have $z>5$.  Of the remaining 15179 quasars with
%%     $0.3<z<5$, 60 quasars have $V_i=0$ and are dropped from the
%%     analysis.  As a result, the green points above contain 15,119
%%     quasars.  The red circles contain 14,953 quasars.}
%%   \label{fig:sdss}
%% \end{figure*}

%% \begin{figure*}
%%   \begin{center}
%%     \includegraphics[width=0.6\textwidth,keepaspectratio]{mcgreer.pdf}
%%   \end{center}
%%   \caption{Comparison with the published LF of
%%     \citet{2013ApJ...768..105M} for $4.7\leq z<5.1$.  There are 148
%%     quasars in their DR7 sample and 52 quasars in the Stripe 82
%%     sample. Of these 1 quasar from the Stripe 82 sample has $V_i=0$.
%%     The published samples of \citet{2013ApJ...768..105M} have 146 and
%%     51 quasars.}
%%   \label{fig:mcgreer}
%% \end{figure*}

@@

%% \begin{figure*}
%%   \begin{center}
%%     \includegraphics[width=\textwidth]{glikman3.pdf}
%%   \end{center}
%%   \caption{Attempts at reproducing Glikman's published LF.  Panels (a)
%%     and (b) use her volume calculations.  Panels (c)--(e) use our
%%     volume calculations.  Various corrections incorporated by Gabor
%%     are in panels (c)--(e).  Red open circles in all panels are
%%     Glikman's published values; I cannot reproduce them in any of the
%%     panels.  All luminosity function in this version of the draft use
%%     Gabor's October data from panel (d).}
%%   \label{fig:glikman}
%% \end{figure*}

%% \begin{figure*}
%%   \begin{center}
%%     \includegraphics[width=\textwidth]{giallongo2.pdf}
%%   \end{center}
%%   \caption{Giallongo's LF when selection function is taken to be
%%     $\phi_\mathrm{corr}/\phi$ from their paper.  This plots shows that
%%     additional correction is required, which has been incorporated in
%%     our LFs.}
%%   \label{fig:giallongo}
%% \end{figure*}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth,keepaspectratio]{q.pdf}
  \end{center}
  \caption{Helium reionization.}
\end{figure*}
